Increasing the topological gap by an order of magnitude through the geometry for Majorana SNS junctions.

### 2019-02-07 paper/snakemajoranas.tex
ref to the parameters

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:setup}.
Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}.\label{fig:bandstuctures}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}.\label{fig:wavefunctions}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
The parameters values are as noted below Eq.~\eqref{eq:hamiltonian}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).
\label{fig:phasediagrams}}
\end{figure}

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}\label{sec:physical_picture}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/bandstructures}
\caption{Figure of the bandstuctures corresponding to the system in Fig.~\ref{fig:setup}.
Blue lines correspond to $\phi=0$, $B=0$ and red lines to $\phi=\pi$, $B = \SI{1}{T}$.
The three subplots are for different amplitudes of the zigzag, with (a) $z_y=0$, (b) $z_y=\frac{W}{4}$, and (c) $z_y=\frac{W}{2}$, where $W=\SI{200}{\nm}$ is the junction width.
We observe that once there are no more straight trajectories inside the junction (when $z_y=\frac{W}{2}$) the spectrum becomes most insensitive to the momentum $k_x$.
The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}.\label{fig:bandstuctures}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/wavefunctions}
\caption{Density of wavefunctions $\left|\psi\right|^2$ for sizes and geometries.
With (a) a straight system, (b) a saw-toothed zigzag system, (c) a system where the normal region is defined by lines parallel to a sinusoid, and (d) similar to (c) but with disordered edges.
Inside the figure, we indicate the Majorana length (or coherence length) $\lambda_\textrm{M}$ and the topological energy gap $E_\textrm{gap}$.
We observe that $\xi$ for (a) is significantly longer and $E_\textrm{gap} = E_\textrm{1} - E_M$ orders of magnitude smaller than for (b), (c), and (d), meaning that the details of the geometry do not matter for the improvements to occur.
The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}.\label{fig:wavefunctions}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=0.95\columnwidth]{figures/phasediagrams}
\caption{Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
Phase diagrams of a straight system (a), (b) and zigzag system (c), (d), where (a), (c) are $E(\mu, B)$ and (b), (d) are $E(\phi, B)$.
We compute the dispersion of the translationally invariant realizations of a straight and saw-toothed zigzag system and find $\min{E(k)}$ to obtain the energy gap.
% Additionally, use a generalized eigenvalue problem to find all phase boundaries at once.
The parameters values are written on the bottom of Sec.~\eqref{sec:physical_picture}, except with $a=\SI{5}{\nm}$ and $L_\textrm{SC}=\SI{800}{\nm}$.
The chemical potential is $\mu=\SI{10}{\meV}$ in (b) and (d) and the superconducting phase is $\phi=\pi$ in (a) and (c).
\label{fig:phasediagrams}}
\end{figure}
